---
title: "Week 9 - Working with Web APIs"
author: "Emilie M Bolduc"
date: "10/29/2017"
output: html_document
---

### Assignment
The New York Times web site provides a rich set of APIs, as described here: http://developer.nytimes.com/docs

You’ll need to start by signing up for an API key.

Your task is to choose one of the New York Times APIs, construct an interface in R to read in the JSON data, and transform it to an R dataframe.

### Solution 

#### Libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(jsonlite)
library(DT)
library(tidyr)
library(dplyr)
```

#### Access NY Times API Data

Get API key from NY Times:
```{r API key}
key <- "&api-key=2989168319214883a9a2a5e3d5713d88"
```

NY Times API used: (/lists/best-sellers/history.json)
```{r NY Times API url}
url <- "https://api.nytimes.com/svc/books/v3/lists/best-sellers/history.json?age-group=4"
```

I want to query the bestseller books for 4-year-olds. I tried to include the AgeGroup value in the fromJSON function below, but kept getting error messages. Eventually had to manually add it to the url above to get it work.
```{r Age Group}
AgeGroup <- "?age-group=4"
```

Use jsonlite [fromJSON] function to get the API data with API key and query for kids books from NY Times:
```{r Access data from API}
rawdata <- fromJSON(paste0(url, key))
```
Reference: https://cran.r-project.org/web/packages/jsonlite/vignettes/json-apis.html

Confirm it worked:
```{r Raw}
head(rawdata)
```
Yay!

#### Review raw data
What class are we dealing with:
```{r Class}
class(rawdata) 
```

How many elements?
```{r}
length(rawdata)
```

Names?
```{r}
names(rawdata)
```

Class of each element?
```{r}
lapply(rawdata, class)
```

How many elements in each list component?
```{r}
lapply(rawdata, length)
```


#### Clean the data before transforming into dataframe
Remove the first 3 lists ("status", "copyright", "num_results"):
```{r}
results <- rawdata[-c(1:3)]
names(results)
length(results)
class(results)
```

#### Turn into a dataframe
```{r}
results_df <- results[["results"]]
```
Confirm:
```{r}
class(results_df)
```
Yay!


#### Tidy data with [dpylr] and [tidyr] packages
```{r}
colnames(results_df)
kidsbooks <- tbl_df(results_df)
kidsbooks <- select(kidsbooks, one_of(c("title", "description", "author", "price", "age_group")))
kidsbooks <- rename(kidsbooks, Title = 'title', Description = 'description', Author = 'author', Price = 'price', Ages = 'age_group')
kidsbooks
```



#### Make a Pretty Table
```{r}
datatable(kidsbooks)
```






